Fasano Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2021-02-16 journalMS/article.tex
updated reference list for additional citations

As a caveat, to the fit produced by Teukolsky and Press are accurate when $N \gtrsim 20$, and the $p$-value is less than (more significant than) $\sim 0.20$. For $p$-value that are $> 0.20$, the distributional approximation may not be accurate. While the assertion the two data sets are \textit{not} significantly different is surely correct; analysis looking to compare $p$-value across experiments conditions -- such as if one was to do a cross study concordant analysis comparing rank order $p$-value \cite{Ness}
%(Cite bmal1 science Article or TimeTrial)
-- would not be possible with the Teukolsky and Press approximate fit. Moreover, additional arguments have been made to the validity of the $>1$-D KS tests as not being distribution-free \citep{Babu2006}.

>>>>

As a caveat, to the fit produced by Teukolsky and Press are accurate when $N \gtrsim 20$, and the $p$-value is less than (more significant than) $\sim 0.20$. For $p$-value that are $> 0.20$, the distributional approximation may not be accurate. While the assertion the two data sets are \textit{not} significantly different is surely correct; analysis looking to compare $p$-value across experiments conditions -- such as if one was to do a cross study concordant analysis comparing rank order $p$-value \citep{Ness-Cohn2020}
%(Cite bmal1 science Article or TimeTrial)
-- would not be possible with the Teukolsky and Press approximate fit. Moreover, additional arguments have been made to the validity of the $>1$-D KS tests as not being distribution-free \citep{Babu2006}.
